Results

### 2025-04-04 notebooks/00_index.qmd
fix: Remove unused imports and extract density ylabel to variable

```{julia}
using Speasy
using SPEDAS
using SPEDAS: ulabel
using DimensionalData
using GLMakie
# using CairoMakie
using Dates
using PartialFunctions
using Unitful, Latexify, UnitfulLatexify, LaTeXStrings
using Beforerr: _theme_legend

@@

B_ylabel = "B (nT)"
B_labels = ["Bx", "By", "Bz", "Magnitude"]
V_ylabel = "Velocity (km/s)"
V_labels = ["Vx", "Vy", "Vz", "Magnitude"]
Temp_ylabel = "Temperature (eV)"
WI_PM_3DP_labels = ["Proton"] # "Proton (3DP, PESA Low)"
WI_ELM2_3DP_labels = ["Electron"] # "Electron (3DP, EESA Low)"

psp_n = SPEDAS.DataSet(
    "Density",
    [
        SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/DENS"; labels=["SPI Proton"]),
        SpeasyProduct("PSP_FLD_L3_RFS_LFR_QTN/N_elec"; labels=["RFS Electron"]),
        SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_density"; labels=["SQTN Electron"])
    ];
    ylabel=ulabel("Density", "cm^-3")
)

@@

wind_n = SPEDAS.DataSet(
    "Density",
    [
        SpeasyProduct("WI_PM_3DP/P_DENS"; labels=WI_PM_3DP_labels),
        SpeasyProduct("WI_ELM2_3DP/DENSITY"; labels=WI_ELM2_3DP_labels)
    ];
    ylabel=ulabel("Density", "cm^-3")
)

>>>>

```{julia}
using Speasy
using SPEDAS
using SPEDAS: ulabel
using DimensionalData
using GLMakie
# using CairoMakie
using Dates
using PartialFunctions
using Beforerr: _theme_legend

@@

B_ylabel = "B (nT)"
B_labels = ["Bx", "By", "Bz", "Magnitude"]
n_ylabel = ulabel("Density", "cm^-3")
V_ylabel = "Velocity (km/s)"
V_labels = ["Vx", "Vy", "Vz", "Magnitude"]
Temp_ylabel = "Temperature (eV)"
WI_PM_3DP_labels = ["Proton"] # "Proton (3DP, PESA Low)"
WI_ELM2_3DP_labels = ["Electron"] # "Electron (3DP, EESA Low)"

psp_n = SPEDAS.DataSet(
    "Density",
    [
        SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/DENS"; labels=["SPI Proton"]),
        SpeasyProduct("PSP_FLD_L3_RFS_LFR_QTN/N_elec"; labels=["RFS Electron"]),
        SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_density"; labels=["SQTN Electron"])
    ];
    ylabel=n_ylabel
)

@@

wind_n = SPEDAS.DataSet(
    "Density",
    [
        SpeasyProduct("WI_PM_3DP/P_DENS"; labels=WI_PM_3DP_labels),
        SpeasyProduct("WI_ELM2_3DP/DENSITY"; labels=WI_ELM2_3DP_labels)
    ];
    ylabel=n_ylabel
)
